On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-10-08 docs/mvfits_paper/mvf.tex
cleaning for submission

\input{src/definitions}
\def\check#1{\red{#1}}
\def\new#1{\blue{#1}}
\def\remove#1{\hlred{#1}}
\newcommand{\cw}{\tilde{\omega}}
\newcommand{\CW}{\tilde{\Omega}}
\newcommand{\CWr}{{\Omega}^{\mathrm{r}}}
\newcommand{\CWc}{{\Omega}^{\mathrm{c}}}
\newcommand{\SC}{\mathcal{K}}
\newcommand{\CC}{\mathcal{C}}
\newcommand{\SCr}{\mathcal{K}^{\mathrm{r}}}
\newcommand{\SCc}{\mathcal{K}^{\mathrm{c}}}
\newcommand{\lalapprox}{\texttt{MMRDNS}}
\def\jf{j_f}
\def\mf{M_f}
\newcommand{\LL}{\bar{l}}
\newcommand{\MM}{\bar{m}}
\def\lmn{_{\ell m n}}
\def\LM{_{\bar{\ell} \bar{m}}}
\def\LMlmn{_{\bar{\ell} \bar{m} \ell m n}}
\def\gmvp#1{greedy-multivariate-polynomial#1
  (\texttt{GMVP}#1)\gdef\gmvp{\texttt{GMVP}}}
\def\gmvr#1{greedy-multivariate-rational#1
  (\texttt{GMVR}#1)\gdef\gmvr{\texttt{GMVR}}}

@@

    \includegraphics[width=0.49\textwidth]{fig/fits_w.pdf} & \includegraphics[width=0.49\textwidth]{fig/fits_tau.pdf}

@@

    \includegraphics[width=0.49\textwidth]{fig/res_w.pdf} & \includegraphics[width=0.49\textwidth]{fig/res_tau.pdf}

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial order will yield satisfactory results (i.e. the well known ``Runge's phenomenon'').

@@

  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}

@@

  \includegraphics[width=0.45\textwidth]{fig/issue3_pgreedy.pdf}

@@

	\input{src/cwfit_eqns}

@@

    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf} \\
    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}

@@

% \section{Algorithms}
% \label{app:algos}
% % \begin{widetext}
% %
% \hspace{1cm}
% {\scriptsize
% \begin{algorithm}[H]
%   %
%   \caption{$\mathcal{A}_{\gmvr}$, the action for \gmvr. Model calculation given basis symbols, and output of model error estimate.}
%   %
%   \label{alg:A_gmvr}
%   \begin{algorithmic}[1]
%     %
%     \State {\bf Input:} \{ $\mlam_{trial}$, $tol=10^{-3}$ \}
%     \vskip 10pt
%     \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
%     \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
%     \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.
%     \State $done = False$
%     \While { not $done$ }
%       \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
%       \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
%       \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
%       \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
%       \State (Implicitly, $n = n+1$)
%     \EndWhile
%     \vskip 10pt
%     \State {\bf Output:} $\epsilon^{(n)}$
%   \end{algorithmic}
% \end{algorithm}
% }
% % \end{widetext}
\newpage
\section{Additional Equations}
\label{app:eqns}

%
% Equations for mixing coefficients
%
\begin{widetext}
  \input{src/ysprod_eqns}
\end{widetext}

@@

% %
% % Plots of QNM frequencies
% \begin{figure*}[htb]
%   %
%   \begin{tabular}{lr}
%     \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
%     \\
%     \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
%   \end{tabular}
%   %
% 	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
%   %
%   Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$. Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
%   %
%   The grey dashed line marks the value of $\kappa$ where $\j{}=0$. Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. (Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}. }
%   %
%   \label{fig:qnm}
%   %
% \end{figure*}
%
% % Plots of mixing coefficients
% \begin{figure*}[htb]
%   %
%   \begin{tabular}{lr}
%     \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf} \\
%     \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
%   \end{tabular}
%   %
% 	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
%   %
%   \label{fig:ys}
%   %
% \end{figure*}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
\newpage
% \bibliographystyle{ieeetr}
\bibliographystyle{mnras}
\bibliography{src/mvf.bib}
\end{document}

>>>>

\input{definitions}
\def\check#1{\red{#1}}
\def\new#1{\blue{#1}}
\def\remove#1{\hlred{#1}}
\newcommand{\cw}{\tilde{\omega}}
\newcommand{\CW}{\tilde{\Omega}}
\newcommand{\CWr}{{\Omega}^{\mathrm{r}}}
\newcommand{\CWc}{{\Omega}^{\mathrm{c}}}
\newcommand{\SC}{\mathcal{K}}
\newcommand{\CC}{\mathcal{C}}
\newcommand{\SCr}{\mathcal{K}^{\mathrm{r}}}
\newcommand{\SCc}{\mathcal{K}^{\mathrm{c}}}
\newcommand{\lalapprox}{\texttt{MMRDNS}}
\def\jf{j_f}
\def\mf{M_f}
\newcommand{\LL}{\bar{l}}
\newcommand{\MM}{\bar{m}}
\def\lmn{_{\ell m n}}
\def\LM{_{\bar{\ell} \bar{m}}}
\def\LMlmn{_{\bar{\ell} \bar{m} \ell m n}}
\def\gmvp#1{greedy-multivariate-polynomial#1
  (\texttt{GMVP}#1)\gdef\gmvp{\texttt{GMVP}}}
\def\gmvr#1{greedy-multivariate-rational#1
  (\texttt{GMVR}#1)\gdef\gmvr{\texttt{GMVR}}}

@@

    \includegraphics[width=0.49\textwidth]{fits_w.pdf} & \includegraphics[width=0.49\textwidth]{fits_tau.pdf}

@@

    \includegraphics[width=0.49\textwidth]{res_w.pdf} & \includegraphics[width=0.49\textwidth]{res_tau.pdf}

@@

Worst, in cases where the underlying dataset is best described by a rational function, no polynomial order will yield satisfactory results (i.e. the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).

@@

  \includegraphics[width=\textwidth]{issue3_summary.pdf}

@@

  \includegraphics[width=0.45\textwidth]{issue3_pgreedy.pdf}

@@

	\input{cwfit_eqns}

@@

    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_2.pdf} \\
    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_4.pdf}

@@

% 
\newpage
\section{Additional Equations}
\label{app:eqns}

%
% Equations for mixing coefficients
%
\begin{widetext}
  \input{ysprod_eqns}
\end{widetext}

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
\newpage
% \bibliographystyle{ieeetr}
\bibliographystyle{mnras}
\bibliography{mvf.bib}
\end{document}
